Legacy Data Confounds Genomics Studies

### 2019-05-02 LatexManuscript/legacy.tex
minor edits
final edits - update 10kb plot

$Q$-associated variants are distributed across the genome, with chromosome 1 showing an excess of such variants, and other chromosomes being relatively uniform (Figure \ref{CountPerChrom}).
At a 10kb scale, we also see rather uniform distribution with a small number of regions showing an enrichment for such variants (Figure \ref{VariantDensity}).
We identify a 10kb region in chromosome 17 has 35 $Q$-associated variants.
Distribution of association statistics in this region is provided in Figure \ref{Top10}.

@@

\begin{figure}[h]
\centering
\includegraphics[width=15cm,keepaspectratio]{../Figures/VariantDensity.jpg}
\caption{The number of $Q$-associated variants per 10kb window across the genome. 
One region in chromosome 17 has more than 10 variants per window.}  
\label{VariantDensity}
\end{figure}

>>>>

$Q$-associated variants are distributed across the genome, with chromosome 1 showing an excess of such variants, and other chromosomes being relatively uniform (Figure \ref{CountPerChrom}).
At a 10kb scale, we also see rather uniform distribution with a small number of regions showing an enrichment for such variants (Figure \ref{VariantDensity}).
While regions flagged by the 1kGP strict mask appear enriched in $Q$-associated variants, we also identify a 10kb region in chromosome 17 has 35 $Q$-associated variants.
Distribution of association statistics in this region is provided in Figure \ref{Top10}.

@@

\begin{figure}[h]
\centering
\includegraphics[width=15cm,keepaspectratio]{../Figures/VariantDensity.jpg}
\caption{The number of $Q$-associated variants per 10kb window across the genome.
Red bars indicate regions within and black bars indicate regions outside the 1kGP strict mask.
One region not flagged by the 1kGP strict mask in chromosome 17 has more than 10 variants per window.}  
\label{VariantDensity}
\end{figure}
